`It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-05-25 manuscript/manuscript-qech-air-quality-tilley.qmd
Submitted manuscript
Update email
Add line numbers, remove highlights

    email: heiko.heilgendorff@gmail.com

@@

@@

      name: Habitat International

@@

      highlights:
        - Low-cost monitors were used to assess air quality at Malawi’s largest hospital
        - Open waste burning is physically extensive and temporally frequent across the hospital campus
        - Air quality measured as PM~2.5~ and PM~10~ consistently exceeded even the most hazardous levels 
        - The most exposed locations were where guardians of patients stay and the HIV clinic

>>>>

    email: heiko@opencitieslab.org

@@

    include-in-header: 
      text: '\usepackage{lineno}\linenumbers'

@@

      name: "Environment International"

@@

### 2023-05-25 manuscript/manuscript-qech-air-quality-tilley.tex
Add line numbers, remove highlights

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Habitat International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={`It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi},
  pdfauthor={Elizabeth Tilley; Hope Chilunga; Jonathan Kwangulero; Lars Schöbitz; Saloni Vijay; Heiko Heilgendorff; Marc Kalina},
  pdfkeywords={waste management, healthcare waste, trash burning, air
quality, Malawi, urbanisation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{`It Is Unbearable To Breath Here': Air Quality, Open
Incineration, And Misinformation In Blantyre, Malawi}
\author[1]{Elizabeth Tilley%
\corref{cor1}%
}
 \ead{tilleye@ethz.ch} 
\author[2]{Hope Chilunga%
%
}
 \ead{hchilunga@poly.ac.mw} 
\author[]{Jonathan Kwangulero%
%
}
 \ead{kwangulero@gmail.com} 
\author[1]{Lars Schöbitz%
%
}
 \ead{lschoebitz@ethz.ch} 
\author[1]{Saloni Vijay%
%
}
 \ead{svijay@ethz.ch} 
\author[3]{Heiko Heilgendorff%
%
}
 \ead{heiko.heilgendorff@gmail.com} 
\author[1]{Marc Kalina%
%
}
 \ead{mkalina@ethz.ch}

@@

\begin{highlights}
\item Low-cost monitors were used to assess air quality at Malawi's
largest hospital\item Open waste burning is physically extensive and
temporally frequent across the hospital campus\item Air quality measured
as PM\textsubscript{2.5} and PM\textsubscript{10} consistently exceeded
even the most hazardous levels\item The most exposed locations were
where guardians of patients stay and the HIV clinic
\end{highlights}

\begin{keyword}
    waste management \sep healthcare waste \sep trash burning \sep air
quality \sep Malawi \sep 
    urbanisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

>>>>

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{lineno}\linenumbers
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Environment International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={`It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi},
  pdfauthor={Elizabeth Tilley; Hope Chilunga; Jonathan Kwangulero; Lars Schöbitz; Saloni Vijay; Heiko Heilgendorff; Marc Kalina},
  pdfkeywords={waste management, healthcare waste, trash burning, air
quality, Malawi, urbanisation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{`It Is Unbearable To Breath Here': Air Quality, Open
Incineration, And Misinformation In Blantyre, Malawi}
\author[1]{Elizabeth Tilley%
\corref{cor1}%
}
 \ead{tilleye@ethz.ch} 
\author[2]{Hope Chilunga%
%
}
 \ead{hchilunga@poly.ac.mw} 
\author[]{Jonathan Kwangulero%
%
}
 \ead{kwangulero@gmail.com} 
\author[1]{Lars Schöbitz%
%
}
 \ead{lschoebitz@ethz.ch} 
\author[1]{Saloni Vijay%
%
}
 \ead{svijay@ethz.ch} 
\author[3]{Heiko Heilgendorff%
%
}
 \ead{heiko@opencitieslab.org} 
\author[1]{Marc Kalina%
%
}
 \ead{mkalina@ethz.ch}

@@

\begin{keyword}
    waste management \sep healthcare waste \sep trash burning \sep air
quality \sep Malawi \sep 
    urbanisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable, frame hidden, sharp corners, interior hidden]}{\end{tcolorbox}}\fi
